\documentclass[11pt]{article}

\usepackage[utf8]{inputenc} % character encoding

% Useful packages
\usepackage{amsmath}		            % lets you input equations in math mode
\usepackage{graphicx}		            % lets you include images
\usepackage{enumerate}		            % lets you make lists
\usepackage{subcaption}                 % if you want to use subcaptions
\usepackage[colorlinks=true]{hyperref}  % for making hyperlinks
\usepackage{hypcap}	                    % makes links refer to figures and not captions
\usepackage{relsize}		            % lets you use relative font sizes
\usepackage{caption}                    % lets you add captions
\usepackage{array}                      % lets you specify table column widths
\usepackage[margin=1in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{float}
\usepackage{tabularx}
\usepackage{textgreek}
\usepackage{amssymb}
\usepackage{amsthm}
\renewcommand{\qedsymbol}{$\blacksquare$}
\usepackage{blindtext}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\begin{document}

\textbf{Find the error and redo:}\\
How many subsets of a 100-element set have more than one element?

\textbf{Solution:} There are $\binom{100}{2}$ subsets of a 100-element set with two elements, since this counts unordered pairs of distinct elements. Similarly, there are $\binom{100}{3}$ subsets with three elements. Continuing in this way and using the sum rule (these cases are mutually exclusive), there are 
\[
\sum_{k=2}^{99}\binom{100}{k}
\]
subsets of a 100-element set that have more than one element.

\textbf{Fixing the error:}\\
A subset $B$ of a set $A$ is valid only if all elements of $B$ are also elements of $A$. Using this definition, note that a subset of a 100-element set can be the set itself. The above solution omitted the 100-element subset. To fix this, change the summation to 
\[
\sum_{k=2}^{100}\binom{100}{k},
\]
which now includes the full 100-element subset.
\textbf{Totally different approach:}\\
Think of the 100-element set $S$ as a bit string of length 100. Any subset of $S$ corresponds to a bit string where a $1$ means the element is included and a $0$ means it is not. Each position has two possibilities, so by the product rule there are $2^{100}$ subsets in total.

Now remove the subsets with exactly one element (there are 100 of them) and the empty subset (one of them). This leaves
\[
2^{100}-100-1=2^{100}-101
\]
subsets of a 100-element set that have more than one element.

\begin{itemize}
\item \textbf{Who Contributed:} Dhvan Shah was the main contributor, doing the formal write-up of the solution. Pranav Bonthu and Michael Ku compared their solutions to Dhvan’s and provided feedback and edits.
\item \textbf{Resources}: No resources were used.
\item \textbf{Main points:} Based on group discussions, we felt that this problem
\end{itemize}

\end{document}